Optimal Particle Paths Around Points in $\R^2$ with Constrained Acceleration

### 2013-09-29 particle_definitions.tex
Add proof of minimizing theta.
Adding some particle definitions.

@@

\begin{definition}
  A n-dimensional particle, $p$, is an object with zero volume that travels along a n-dimensional path. Traveling along a path means that the particle is at position $\lambda(t)$ at time $t$, for all $t \in [0, T_{f,\lambda}]$. The particle may have conditions on its position, velocity, and acceleration in $\R^n$.
\end{definition}

>>>>

\begin{definition}
  A n-dimensional particle, $p$, is an object with zero volume that travels along a n-dimensional path. Traveling along a path means that the particle is at position $\lambda(t)$ at time $t$, for all $t \in [0, T_{f,\lambda}]$. 
\end{definition}

\begin{definition}
A description of a particle $p$ is a set $D(t)$ which contains a particle's position $\vec{x} \in \mathrm{R}^n$ and its derivatives at some time $t$.
\end{definition}

\begin{definition}
A condition $c$ on a particle $p$ is a boolean function $c: \mathrm{D} \to \{0,1\}$ which takes as input a description $D(t)$ of the particle $p$ at some time $t$. We call a condition satisfied if the condition's output is $1$ at time $t$.
\end{definition}

@@
